---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
First lets download the data, uzip it and put it in a variable **data**

```{r echo = TRUE}
temp <- tempfile()
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",temp)
data <- read.csv(unz(temp, "activity.csv"))
unlink(temp)
```

## What is mean total number of steps taken per day?
As per the instructions:
1. Calculate the total number of steps taken per day (We're are going to store this in a variable called totalStepPerDay for safe keeping)
```{r echo = TRUE}
totalStepPerDay <- aggregate(steps ~ date, data, sum)
```
2. Make a histogram of the total number of steps taken each day (We'll do this using hist())
```{r echo = TRUE}
hist(totalStepPerDay$steps, breaks=50, main="Histogram of Total steps taken per day")
```
3. Calculate and report the mean and median of the total number of steps taken per day
```{r echo = TRUE}
mean(totalStepPerDay$steps)
median(totalStepPerDay$steps)
```

## What is the average daily activity pattern?
Now we're going to make a time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r echo = TRUE}
## average number of steps taken per interval
averageStepPerInterval <- aggregate(steps ~ interval, data, mean)

plot(averageStepPerInterval$interval, averageStepPerInterval$steps, type='l', xlab= '5 min. interval', ylab= 'average # of steps taken', col='blue', main='Time series of average steps taken during each 5min. interval', lwd=2)
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r echo = TRUE}
averageStepPerInterval[averageStepPerInterval$steps==max(averageStepPerInterval$steps),1]
```

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
